---
title: "Building Research Leaders for Early Career Researchers"
subtitle: "Evaluation (November 2024)"
# author: "Jen Beaudry"
# date: "2024-04-12"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

```

```{r library, include=FALSE}

# devtools::install_github("adletaw/captioner")

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)
library(captioner)

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

source(here("..", "functions", "meta_rename.R"))
source(here("..", "functions", "ratings_summary.R"))

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "brl_eval_processed_data.csv"), lazy = FALSE)

```

```{r code factors, include=FALSE}


# turn all ratings variables into factors, use datapasta to do this!
# the code below works

df$expectations <- factor(df$expectations, levels = c("Exceeded my expectations", "Met my expectations", "Partly met my expectations", "Did not meet my expectations"))
df$post_phd <- factor(df$post_phd, levels = c("Less than 5 years post-PhD", 
                                                  "5 to 10 years post-PhD", 
                                                  "11 to 15 years post-PhD"))
                                               #   "More than 15 years post-PhD" [no one]

# work with all rating items together because they have the same levels

cols <- c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement")


# turn the cols columns into factors
df <- df %>% 
  mutate(across (all_of(cols), ~factor(., 
                                       levels = c("N/A", 
                                           "Strongly disagree",
                                           "Somewhat disagree",
                                           "Neither agree nor disagree",
                                           "Somewhat agree",
                                           "Strongly agree"))))

```

```{r captions, include = FALSE}

table_nums(name = "career_stage", 
           caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'")

table_nums(name = "info_workshop", 
           caption = "'What did you expect from this workshop?'")

table_nums(name = "expectations", 
           caption = "'Please elaborate on how the workshop aligned with your expectations.'")

table_nums(name = "action", 
          caption = "'Did this workshop inspire you to take any immediate action(s)?'")

table_nums(name = "success",
             caption = "'Do you credit any research successes to the workshop?'")

table_nums(name = "best_parts",
             caption = "'What were the best parts of the workshop?'")

table_nums(name = "improvement",
             caption = "'Any suggestions for improvement?'")

table_nums(name = "anything_else",
             caption = "'Anything else you want us to know?'")

table_nums(name = "attendance", 
           caption = "We asked participants to explain why they attended the number of sessions that they did.")

fig_nums(name = "ratings_summary", 
         caption = "Ratings of different aspects of the workshop")

```



```{r sessions attendance}

participants <- 21

#breadcrumb for caption: \captionsetup[table]{labelformat=empty}
# that's if I include header use caption in the yaml

```


Hugh Kearns from ThinkWell designed and delivered the 
*Building Research Leaders for Early Career Researchers* workshop. This workshop 
was run as series of three full-day sessions from April to October 2024. 
Of the `r participants` participants in the workshop, `r nrow(df)` completed this evaluation.

On average, the respondents to this survey attended `r round(mean(df$attendance),2)` 
of the 3 sessions, with everyone attending at least `r min(df$attendance)` sessions.
Their explanations for why they attended the sessions that they did are shown in 
`r table_nums("attendance", display = "cite")` in the Appendix. 

We asked participants to rate a number of items about the workshop and the trainer 
on a scale from 'strongly disagree' to 'strongly agree' (see 
`r fig_nums(name = "ratings_summary", display = "cite")`).

\
`r fig_nums(name = "ratings_summary")`

```{r creating tibbles for all ratings, include = FALSE}

# get total n to calculate percentages

total_n <- length(df$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

ratings <- df %>% 
  select (c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement"))

# UPDATE THE COLUMNS PARAMETER WITH THE STRINGS FROM ABOVE

columns <- c("research_leadership",
  "research_productivity",
  "expert",
  "engaging",
  "balance",
  "current_role",
  "future_roles",
  "reengagement")

# RUN THE FUNCTION & APPLY TO ALL COLUMNS IN OUR DF

ratings_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(ratings, column)
})

# remove the NA responses
ratings_summary <- na.omit(ratings_summary)


# also, figure out how many responded with the agree ratings. I use these in the 
  # text summaries later

# [breadcrumb: can I use apply for this too?? need to do this later!]

agree <- c("Strongly agree", "Somewhat agree")


```

```{r plot the ratings}

# Relevel the responses [changes order in ggplot, but not the dataframe]
# plot it first to see if I need to do this

# tor_rating$rating <- factor (rating$rating, levels = c("Strongly agree",
#                                            "Somewhat agree",
#                                            "Neither agree nor disagree",
#                                            "Somewhat disagree",
#                                            "Strongly disagree"))

# put them in reverse order of how I want them to appear
ratings_summary$rating_item <-
  factor (
    ratings_summary$rating_item,
    levels = c(
      "reengagement", 
      "future_roles",
      "current_role",
      "balance",
      "engaging",
      "expert",
      "research_leadership",
      "research_productivity"
    )
  )

# [breadcrumb] I can delete this later, but this is useful to create the plot_labs

# labs <- meta %>%
#   filter(scale == "common_ratings") %>%
#   pull(item_text_short) %>%
# datapasta::vector_paste_vertical()


# plot it


ggplot(ratings_summary, aes(fill = rating, y = percentage, x = rating_item)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(
    palette = "Blues",
    na.value = "grey50",
    direction = 1,
    labels = c(
      "N/A",
      "Strongly disagree",
      "Somewhat disagree",
      "Neither agree nor disagree",
      "Somewhat agree",
      "Strongly agree"
    )
  ) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_x_discrete(
    labels = c(
      "I would attend another workshop \nfrom this trainer",
      "I expect that the content will be \nuseful in my future role(s)",
      "The workshop content was relevant \nto my current role",
      "The workshop had a good balance \nof group discussion and presentation",
      "The trainer was very engaging",
      "The trainer is an expert in \nthe sector",
      "The workshop provided me with \na greater understanding of \nresearch leadership",
      "The workshop provided me with \nstrategies to increase my \nresearch productivity"
 )
) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

# FYI: the labels are always in opposite directions from the data set!

```

\newpage

```{r expectations data, include = TRUE}

expect <- df %>% 
    dplyr::group_by (expectations) %>% 
  count()

```

```{r careerstage table, include = TRUE}

# remove the post-PhD because it's repeated in every response
df$post_phd <- str_remove(df$post_phd, " post-PhD")


years <- df %>% 
    dplyr::group_by (post_phd) %>% 
  count()

# change the text to be used in the markdown
years$post_phd <- str_replace(years$post_phd, "Less", "less")

career_stage <- df %>% 
  select(c(id, post_phd, careerstage_yes, careerstage_no)) %>% 
  replace_na(list(careerstage_yes = "", careerstage_no = "")) %>% 
  arrange(desc(post_phd))


kable(
  career_stage,
  booktabs = T, 
  align = c('clll'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'",
  col.names = c("Respondent", "Years post PhD", "Reasons why it was appropriate", "Reasons why it was not appropriate")
  ) %>%
  column_spec (column = 3, width = "5cm") %>%
   column_spec (column = 4, width = "5cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

We had a mix of participants in this workshop (nominated by their Deans of Research). 
The respondents to the survey reflected this mix; `r years[2,2]` respondents
were `r years [2,1]` post-PhD and `r years[1,2]` respondents were `r years [1,1]` post-PhD. 

The respondents varied as to whether the program met their expectations: 

  * `r expect [1,2]` (`r round((expect[1,2]/nrow(df))*100,2)`%) respondents 
indicated that the program exceeded their expectations,
  * `r expect [2,2]` (`r round((expect[2,2]/nrow(df))*100,2)`%) respondents 
indicated that the program met their expectations,
  * `r expect [3,2]` (`r round((expect[3,2]/nrow(df))*100,2)`%) respondents 
indicated that the program partly met their expectations, and 
  * `r expect [4,2]` (`r round((expect[4,2]/nrow(df))*100,2)`%) respondents 
indicated that the program did not meet their expectations. 

`r table_nums("info_workshop", display = "cite")` reports what the respondents
said they expected from the workshop. Their explanations of how the program aligned with their expectations are shown 
in `r table_nums("expectations", display = "cite")`. 

```{r info_workshop table, include = TRUE}

info_workshop <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, info_workshop) %>% 
  filter (!is.na(info_workshop))


kable(
  info_workshop,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What did you expect from this workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

```{r expectations table, include = TRUE}

expectations <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expect_comment) %>% 
  filter (!is.na(expect_comment))


kable(
  expectations,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on how the workshop aligned with your expectations.'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

```{r action table, include = TRUE}

action <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, actions) %>% 
  filter (!is.na(actions))


kable(
  action,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Did this workshop inspire you to take any immediate action(s)?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

```{r success table, include = TRUE}

success <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, success) %>% 
  filter (!is.na(success))


kable(
  success,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Do you credit any research successes to the workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

```{r best_parts table, include = TRUE}

best <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, best_parts) %>% 
  filter (!is.na(best_parts))

kable(
  best,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What were the best parts of the workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```


```{r improvement table, include = TRUE}

improve <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, improvement) %>% 
  filter (!is.na(improvement))


kable(
  improve,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Any suggestions for improvement?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

```{r anything else table, include = TRUE}

anything_else <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, anything_else) %>% 
  filter (!is.na(anything_else))


kable(
  anything_else,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Anything else you want us to know?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))


```

# Appendix

```{r attendance table, include = TRUE}


attendance <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, attendance_text) %>% 
  filter (!is.na(attendance_text))


kable(
  attendance,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "We asked participants to explain why they attended the number of sessions that they did.",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))



```

If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 

